{\bf {\Large Four decades of water quality change in the upper San Francisco Estuary}}

### 2016-12-09 sftrends_manu.Rnw
fig 5 now only tot nitrogen

<<stock, fig.height = 5, fig.width = 8, cache = T, out.width = '\\textwidth', fig.cap = 'Nitrogen concentration measurements (mg L$^{-1}$) from the City of Stockton Wastewater Treatment Plant, San Joaquin County.  Wastewater discharge requirements were implemented in 2006 for nitrification/denitrification and tertiary filtration to convert ammonium to nitrate.'>>=
data(stock_conc)

@@

ylab1 <- expression(paste("Total nitrogen (mg ", L^-1, ")"))
ylab2 <- '% of total nitrogen'
xrng <- range(c(toplo1$date, toplo2$date))
yrng <- c(0, 50)
leglabs <- list(
  expression(NH [4] ^ '+'),
  expression(NO [2] ^ '-'),
  expression(NO [3] ^ '2-')
  )

@@

p1 <- ggplot(toplo1) + 
  geom_line(colour = lncol, aes(x = date, y = TN)) + 
  scale_x_date(expand = c(0, 0), limits = xrng) + 
  scale_y_continuous(ylab1, expand = c(0, 0), limits = yrng) + 
  geom_vline(xintercept = as.numeric(lndate), linetype = 'dashed') +
  geom_label_repel(
    data = data.frame(x = lndate, y = 35), 
    aes(x, y, label = 'WWTP upgrades'), 
    box.padding = grid::unit(2, "lines"), 
    nudge_x = 1
    ) + 
  ptheme

p2 <- ggplot(toplo2) + 
  geom_area(aes(x = date, y = val, group = var, fill = var), stat = 'identity', position = 'fill') + 
  scale_x_date(expand = c(0, 0), limits = xrng) + 
  scale_fill_brewer(palette = 'Blues', labels = leglabs) + 
  geom_vline(xintercept = as.numeric(lndate), linetype = 'dashed') +
  scale_y_continuous(ylab2, expand = c(0, 0)) + 
  ptheme + 
  theme(
    legend.position = 'top', 
    legend.title = element_blank()
    )

grid.arrange(pA, pB, ncol = 1, heights = c(0.8, 1))
@

>>>>

<<stock, fig.height = 3, fig.width = 8, cache = T, out.width = '\\textwidth', fig.cap = 'Nitrogen concentration measurements (mg L$^{-1}$) from the City of Stockton Wastewater Treatment Plant, San Joaquin County.  Wastewater discharge requirements were implemented in 2006 for nitrification/denitrification and tertiary filtration to convert ammonium to nitrate.'>>=
data(stock_conc)

@@

ylab1 <- expression(paste("Total nitrogen (mg ", L^-1, ")"))
xrng <- range(c(toplo1$date, toplo2$date))
yrng <- c(0, 50)
leglabs <- list(
  expression(NH [4] ^ '+'),
  expression(NO [2] ^ '-'),
  expression(NO [3] ^ '2-')
  )

@@

p1 <- ggplot(toplo2) + 
  geom_area(aes(x = date, y = val, group = var, fill = var), stat = 'identity', position = 'stack') + 
  scale_x_date(expand = c(0, 0), limits = xrng) + 
  scale_fill_brewer(palette = 'Blues', labels = leglabs) + 
  geom_vline(xintercept = as.numeric(lndate), linetype = 'dashed') +
  geom_label_repel(
    data = data.frame(x = lndate, y = 35), 
    aes(x, y, label = 'WWTP upgrades'), 
    box.padding = grid::unit(2, "lines"), 
    nudge_x = 1
    ) +
  scale_y_continuous(ylab1, expand = c(0, 0)) + 
  ptheme + 
  theme(
    legend.position = 'top', 
    legend.title = element_blank()
    )

p1
@
